How to Learn Useful Changes to Software Projects\\(to Reduce Runtimes and Software Defects)

### 2015-08-22 Manuscript.tex
Updates from ShareLaTeX

Of course, there are many more ways than these four
to generate recommendations on how to change projects.
But the goal of this paper is not to claim that (e.g.) Method4 is some absolute best algorithm. Rather, it is
to offer an evaluation strategy that  can assess alternate proposals for generating
plans. Our hope is that other   researchers repeat our experiments in order to repeat and/or improve
and/or refute our results. To that end, all our materials and data sets are available on-line.

@@

>>>>

Of course, there are many more ways than these four
to generate recommendations on how to change projects.
But the goal of this paper is not to claim that (e.g.) Method4 is some absolute best algorithm. Rather, it is
to offer an evaluation strategy that  can assess alternate proposals for generating
plans. Our hope is that other   researchers apply this strategy  to repeat and/or improve
and/or refute our results. To that end, all our materials and data sets are available on-line, see
github.com/ai-se/XTREES.

@@

  See github.com/ai-se/XTREES\#datafor full access to the Jurecko and Siegmund data.
